---
title: "BRCA.210406"
author: "Siwakorn"
date: "2021/4/6"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Library
```{r}
library(Seurat)
library(tidyverse)
library(rcartocolor)
library(viridis)
library(ggrepel)
```

#Col
```{r}
color_orange = scale_color_gradientn(colours = c("grey","yellow","orange","red"), values = c(0,0.1,0.5,1))
scale_SummaerSea = scale_color_gradientn(colours = c("#173F5F","#20639B","#3CAEA3","#F6D55C","#ED553B"))
col_SummaerSea = c("#173F5F","#20639B","#3CAEA3","#F6D55C","#ED553B")
scale_SummaerSea2 = scale_color_gradientn(colours = c("#6F42AF","#173F5F","#20639B","#3CAEA3","#F6D55C","#ED553B"))
col_SummaerSea2 = c("#6F42AF","#173F5F","#20639B","#3CAEA3","#F6D55C","#ED553B")

color_ig = scale_color_gradientn(colours = c("grey","#120078","#9d0191","#fd3a69","#fecd1a"), values = c(0,0.1,0.3,0.6,1))
col_LemonTree <- c("grey", rcartocolor::carto_pal(6, name = "ag_GrnYl") )
col_viridis <- c("grey",c(viridis::viridis(6))[1:5],"#fecd1a" )
col_RedBlue1 <- scale_fill_gradient2(mid="#FBFEF9",low="#0C6291",high="#A63446",space = "Lab",name="Scale Expression" ,na.value = "white")
col_RedBlue2 <- scale_fill_gradient2(mid="#FBFEF9",low="#2c75ab",high="#e2413b",space = "Lab",name="Scale Expression" ,na.value = "white") 
```

#Instant command
```{r}
Dot_axis90 = theme(axis.text.x =  element_text(size = 15, angle = 90, hjust = 1, vjust = 0.3,color = "black"), axis.text.y = element_text(size = 15)) 
Dot_scale = scale_size(range = c(1.5,8),name = "Percent Expression") 

find <- function(x){
      rownames(scBRCA1)[grep(x,rownames(scBRCA1) )]
}


date = "210413"
fig <-function(x){
  paste0("/home/siwakorn/BRCA/Fig/210413_Identity/scBRCA1.",x,".",gsub("-","", Sys.Date()),".png" )
}
dir.create("/home/siwakorn/BRCA/Fig/210413_Identity/")
```


#Create seurat object
```{r}
data.dir = c(
      "/yshare1/ZETTAI_path_WA_slash_home_KARA/home/siwakorn/BRCA/CellRangerOut/BRCA1_CD45/filtered_feature_bc_matrix/",
      "/yshare1/ZETTAI_path_WA_slash_home_KARA/home/siwakorn/BRCA/CellRangerOut/BRCA1_EP4/filtered_feature_bc_matrix/"
)

BRCA <- list()
name = c("CD45","EP4")
for(i in 1:2 ){
      tmp = Read10X(data.dir = data.dir[i]  )
      BRCA[[i]] <- CreateSeuratObject(counts = tmp, project = name[i], min.cells = 3, min.features = 0)
      BRCA[[i]][["percent.mt"]] <- PercentageFeatureSet(BRCA[[i]], pattern = "^MT-")
      BRCA[[i]]$Batch <- "scBRCA1"
      BRCA[[i]]$DecontX <- "No"
}


Decontx.dir = c(
      "/yshare1/ZETTAI_path_WA_slash_home_KARA/home/siwakorn/BRCA/DecontX/BRCA1/Filtered/BRCA1_no1_decontx_result.rds",
      "/yshare1/ZETTAI_path_WA_slash_home_KARA/home/siwakorn/BRCA/DecontX/BRCA1/Filtered/BRCA1_no2_decontx_result.rds",
      "/yshare1/ZETTAI_path_WA_slash_home_KARA/home/siwakorn/BRCA/DecontX/BRCA1/Filtered/BRCA1_no1.filter.Count500.Mt10_decontx_result.rds",
      "/yshare1/ZETTAI_path_WA_slash_home_KARA/home/siwakorn/BRCA/DecontX/BRCA1/Filtered/BRCA1_no2.filter.Count500.Mt10_decontx_result.rds",
      "/yshare1/ZETTAI_path_WA_slash_home_KARA/home/siwakorn/BRCA/DecontX/BRCA1/Raw/BRCA1_no1.Raw.Count54-65_decontx_result.rds",
      "/yshare1/ZETTAI_path_WA_slash_home_KARA/home/siwakorn/BRCA/DecontX/BRCA1/Raw/BRCA1_no2.Raw.Count54-65_decontx_result.rds"
)
m =1
i= 3
Decontx = c("NaiveFiltered","NaiveFiltered","Count500Mt10","Count500Mt10","Raw.Count54-65","Raw.Count54-65")
name = c("CD45","EP4","CD45","EP4","CD45","EP4")
for(i in 3:8){
      tmp = readRDS(file = Decontx.dir[m])
      BRCA[[i]] <- CreateSeuratObject(counts = tmp$resList$estNativeCounts , project = name[m], min.cells = 3, min.features = 0)
      BRCA[[i]][["percent.mt"]] <- PercentageFeatureSet(BRCA[[i]], pattern = "^MT-")
      BRCA[[i]]$Batch <- "scBRCA1"
      BRCA[[i]]$DecontX <- Decontx[m]
      m=m+1
}

BRCA[[7]][[]]
saveRDS(BRCA, file = paste0(folder,"scBRCA1.SeuratObject.210412.rds"))
```


Processed script : Integration.210412.r
#DecontX benchmark
```{r}
scBRCA1 <- readRDS("/yshare1/ZETTAI_path_WA_slash_home_KARA/home/siwakorn/BRCA/RDS/scBRCA1.DecontXComparison.210412.rds")

Idents(scBRCA1) <- scBRCA1$integrated_snn_res.0.3
DimPlot(scBRCA1, label =T)
table(scBRCA1$orig.ident, scBRCA1$DecontX)

DE.DEcont <- list()
set = c("No-NaiveFiltered", "NaiveFiltered-Raw54.65")
DefaultAssay(scBRCA1) <- "RNA"
for(i in 1:2){
      scBRCA1.sub <- subset(scBRCA1, idents = i )
      Idents(scBRCA1.sub) <- scBRCA1.sub$DecontX
      levels(Idents(scBRCA1.sub))
      name = paste0("Cluster",i, ".",set[1])
      DE.DEcont[[name]] = FindMarkers(scBRCA1.sub, ident.1 = "No",ident.2 = "NaiveFiltered",logfc.threshold = 0.01  )
      name = paste0("Cluster",i, ".",set[2])
      DE.DEcont[[name]] = FindMarkers(scBRCA1.sub, ident.1 = "NaiveFiltered"  ,ident.2 = "Raw.Count54-65",logfc.threshold = 0.01 )
}
for(i in 1:4){
      tmp = DE.DEcont[[i]] %>% as_tibble(rownames ="Gene")
      tmp <- arrange(tmp, desc(avg_logFC))
      tmp$used <- c(rep("Label",10),rep("Unlabel",nrow(tmp)-20), rep("Label",10) )
      tmp$logPvalue = (-1)*log(tmp$p_val,base=1000)
      png(filename = fig(paste0("Volcano.",names(DE.DEcont)[i]) ) , width = 7, height = 8, units="in",res=200)
      border = max(tmp$avg_logFC,-(min(tmp$avg_logFC)) )
    print(
      ggplot(tmp, aes(x = avg_logFC, y = logPvalue, color = used, size = used )) + 
        geom_point() +
        scale_color_manual(values = c("firebrick2","black"))+ #select gray65 or black
        scale_size_manual(values = c( 1.5, 0.75) ) +
        theme_linedraw(base_size = 40)+
        theme(text=element_text(size = 12))+
        geom_vline(xintercept = c(-0.3,0.3)) +
        geom_hline(yintercept = c(2)) +
        xlim(-border,border) +
        ylab("- log1000(p-value)") +
        geom_text_repel(size =6,fontface ="bold", data = subset(tmp, used == "Label"),aes(label = Gene, hjust = 1.2)) +
        NoLegend()
      )
  dev.off()
 }
     
```
#-----Clustering and Identification-------
##Load Dataset
```{r}
scBRCA1 <- readRDS("/yshare1/ZETTAI_path_WA_slash_home_KARA/home/siwakorn/BRCA/RDS/scBRCA1.DecontXFilterRead.210406.rds")
Idents(scBRCA1) <- scBRCA1$integrated_snn_res.0.5
DimPlot(scBRCA1, label =T)
```

##Identity
```{r,fig.width=10}
SignatureGenes = list(
  "DC" = c("CCR7","LAMP3","CCL22","CCL17","CLEC9A","BATF3", "LGALS2","CD1A","CD1C","CD1E","NLRP3","CLEC4C","LRRC26","SCT"),
  "Lym" = c("KLRC1","KLRF1","XCL1","XCL2","IFNG","CCL5","NCR3","CD3G","CD3E","CD8A","CTLA4","FOXP3"),
  "My" = c("C1QC","C1QA","CD14","SPP1","CD68"),
  "B" = c("FCRL5","CD79A","IGHG4"),
  "Other" = c("ANGPT1","COL10A1","KRT15","AGER","VWF","PECAM1","CDH5","KIT","TPSB2","HDC") 
)%>% unlist() %>% as.character()
selected.genes = c("CD3D","CD3G","CCL5","GZMA","NKG7","CD14","LYZ","S100A9","C1QC","IL1B",
                   "CLEC9A","BATF3","XCR1","IRF8","CD1E","CD1A","HLA-DQA2","HLA-DQB2","CD207",
                   "LILRA4","IRF7","CLEC4C",
                   "IGHM","CD79A","IGHD",
                   "TPSB2","KIT","HDC","CSF1",
                   "VWF","COL4A1","PECAM1",
                   "S100A14","KRT8","KRT18","KRT19",
                   "AL022069.1","AC087239.1","HSPA2","PLK2","MKI67")
                   "PTGS1","PTGS2","PTGER2","PTGER4")
DefaultAssay(scBRCA1) <-"RNA"

selected.genes = unlist(SignatureGenes)
DotPlot(scBRCA1, features = selected.genes) + scale_SummaerSea2  +Dot_scale+Dot_axis90
scBRCA1 <- RenameIdents(scBRCA1, 
                        '0' = "T_cell",
                        '1' = "Myeloid",
                        '2' = "Myeloid",
                        '3' = "T_cell",
                        '4' = "T_cell",
                        '5' = "Myeloid",
                        '6' = "Myeloid",
                        '7' = "Unk1",
                        '8' = "Mast_cell",
                        '9' = "T_cell",
                        '10' = "T_cell",
                        '11' = "T_cell",
                        '12' = "T_Proliferating",
                        '13' = "cDC2",
                        '14' = "cDC1",
                        '15' = "B_cell",
                        '16' = "pDC",
                        '17' = "Endothelial",
                        '18' = "LQ")
DimPlot(scBRCA1)
                        

scBRCA1$Identity.Primary <- factor(Idents(scBRCA1), levels = c("T_cell","T_Proliferating","Myeloid","cDC1","cDC2","pDC","B_cell","Mast_cell","Endothelial","Unk1","LQ"))
Idents(scBRCA1) <- scBRCA1$Identity.Primary

saveRDS(scBRCA1,file = "/yshare1/ZETTAI_path_WA_slash_home_KARA/home/siwakorn/BRCA/RDS/scBRCA1.NaivedFilertedDecontX.Identity.Primary.210413.rds")
```


```{r,fig.width=10}
selected.genes = selected.genes
for(i in selected.genes ){
      print(
            FeaturePlot(scBRCA1, features = i)
      )
}


```

```{r}
for(i in selected.genes ){
      print(
            VlnPlot(scBRCA1, features = i)
      )
}


```


##QC Per cluster
```{r}
df = FetchData(scBRCA1, vars = c("nCount_RNA","nFeature_RNA","percent.mt","integrated_snn_res.0.5","Identity.Primary"))
df$CG <- df$nCount_RNA/df$nFeature_RNA
ggplot(df, aes(x= integrated_snn_res.0.5, y = percent.mt )) + geom_jitter() + geom_violin(scale = "width") 
ggplot(df, aes(x= integrated_snn_res.0.5, y = nCount_RNA )) + geom_jitter() + geom_violin(scale = "width")
ggplot(df, aes(x= integrated_snn_res.0.5, y = nFeature_RNA )) + geom_jitter() + geom_violin(scale = "width")


df = FetchData(scBRCA1, vars = c("nCount_RNA","nFeature_RNA","percent.mt","integrated_snn_res.0.5","Identity.primary"))

for(i in c("percent.mt","nCount_RNA","nFeature_RNA")){
      png(filename = paste0("/home/siwakorn/BRCA/Fig/210407_IdentityPrimary_DecontXComparison/scBRCA1.Identity.Primary.QC.",i,".png"), width = 8, height =5, units = "in",res =200)
      print(
            ggplot(df, aes_string(x= "Identity.primary", y = i )) + geom_jitter() + geom_violin(scale = "width") +
                  Dot_axis90 +
                  theme(axis.title.y = element_text(size =15,color = "black"))
      )
      dev.off()
}
ggplot(df, aes(x= Identity.Primary, y = percent.mt )) + geom_jitter() + geom_violin(scale = "width") 
ggplot(df, aes(x= Identity.Primary, y = nCount_RNA )) + geom_jitter() + geom_violin(scale = "width")
ggplot(df, aes(x= Identity.Primary, y = nFeature_RNA )) + geom_jitter() + geom_violin(scale = "width")
ggplot(df, aes(x= Identity.Primary, y = CG )) + geom_jitter() + geom_violin(scale = "width")

```



```{r, fig.width=10}
DimPlot(scBRCA1,label =T) + NoLegend()

length(SignatureGenes)
SignatureGenes
DotPlot(scBRCA1, features = SignatureGenes ) + Dot_axis90
DotPlot(scBRCA1, features = c("CD3D","ITGAM"))

rownames(scBRCA1)[grep("MT-", rownames(scBRCA1))]
DotPlot(scBRCA1, features = c("MT-ND1","MT-ND2","MT-CO1","MT-CO2"))
DotPlot(scBRCA1, features = c("MKI67","MT-ND2","MT-CO1","MT-CO2"))
m21 <- FindMarkers(scBRCA1, ident.1 = "21")
m21 %>% arrange(desc(avg_logFC))
```
##DoubletFinder
```{r}
library("DoubletFinder")
object <- readRDS(file = paste0(folder,"scBRCA1.SeuratObject.210412.rds"))
object <- list(object[[3]],object[[4]])
for(i in 1:2){
	object[[i]] <- subset(object[[i]], nCount_RNA > 500 & percent.mt < 10 )
	object[[i]] <- NormalizeData(object[[i]] )
	object[[i]] <- FindVariableFeatures(object[[i]] , selection.method = "vst", nfeatures = 2000)
	object[[i]] <- ScaleData(object[[i]] )
      object[[i]] <- RunPCA(object[[i]])
      object[[i]] <- RunUMAP(object[[i]], dims = 1:10)
}

saveRDS(object, file = "/yshare1/ZETTAI_path_WA_slash_home_KARA/home/siwakorn/BRCA/RDS/scBRCA1.PreDoubletFinder.210413.rds")


library("DoubletFinder")
object.list <- readRDS(file = "/yshare1/ZETTAI_path_WA_slash_home_KARA/home/siwakorn/BRCA/RDS/scBRCA1.PreDoubletFinder.210413.rds" )
scBRCA1 <- readRDS(file = "/yshare1/ZETTAI_path_WA_slash_home_KARA/home/siwakorn/BRCA/RDS/scBRCA1.NaivedFilertedDecontX.Identity.Primary.210413.rds" )
resultA <- list()
resultB <- list()
for(i in 1){
      DimPlot(object)
      object = object.list[[i]]
	object <- subset(object, nCount_RNA > 500 & percent.mt < 10 )
	object <- NormalizeData(object )
	object <- FindVariableFeatures(object , selection.method = "vst", nfeatures = 2000)
	object <- ScaleData(object )
      object <- RunPCA(object)
      object <- RunUMAP(object, dims = 1:10)
## pK Identification (no ground-truth) ---------------------------------------------------------------------------------------
sweep.res.list <- paramSweep_v3(object, PCs = 1:10, sct = FALSE)
print("A1")
sweep.stats <- summarizeSweep(sweep.res.list, GT = FALSE)
print("A2")
bcmvn <- find.pK(sweep.stats)
print("A")
## Homotypic Doublet Proportion Estimate -------------------------------------------------------------------------------------
Meta = scBRCA1[[]] %>% dplyr::select(Identity.Primary)
CB <- paste0(colnames(object),"_",i)
annotations <- Meta[CB,] 
homotypic.prop <- modelHomotypic(annotations)           ## ex: annotations <- object@meta.data$ClusteringResults
print("B1")
nExp_poi <- round(0.075*nrow(object@meta.data))  ## Assuming 7.5% doublet formation rate - tailor for your dataset
print("B2")
nExp_poi.adj <- round(nExp_poi*(1-homotypic.prop))
print("B")
## Run DoubletFinder with varying classification stringencies ----------------------------------------------------------------
resultA[[i]] <- doubletFinder_v3(object, PCs = 1:10, pN = 0.25, pK = 0.09, nExp = nExp_poi, reuse.pANN = FALSE, sct = FALSE)
#resultB[[i]] <- doubletFinder_v3(object, PCs = 1:10, pN = 0.25, pK = 0.09, nExp = nExp_poi.adj, reuse.pANN = "pANN_0.25_0.09_913", sct = FALSE)
}
resultA[[i]][[]]
saveRDS(resultA, file = "/yshare1/ZETTAI_path_WA_slash_home_KARA/home/siwakorn/BRCA/RDS/scBRCA1.DoubletFinder.ResA.210413.rds" )
#saveRDS(resultB, file = "/yshare1/ZETTAI_path_WA_slash_home_KARA/home/siwakorn/BRCA/RDS/scBRCA1.DoubletFinder.ResB.210413.rds" )


```
##Where is doublet
```{r}
tmp = resultA[[1]][[]] %>% as_tibble(rownames = "CB") %>% dplyr::select(CB, DF.classifications_0.25_0.09_353)
tmp$CB <- paste0(tmp$CB, "_1")
colnames(tmp) = c("CB","DF")
tmp2 = scBRCA1[[]] %>% as_tibble(rownames = "CB")  %>% filter(!CB %in% tmp$CB)
tmp2$DF <- "NoData"
tmp2 <- dplyr::select(tmp2,CB, DF)
tmp <- rbind(tmp, tmp2)
tmp
tmp3 <- tmp$DF 
names(tmp3) <- tmp$CB
scBRCA1 <- AddMetaData(scBRCA1, metadata = tmp3, col.name = "DF")
Idents(scBRCA1) <- scBRCA1$DF
DimPlot(scBRCA1)
table(scBRCA1$Identity.Primary, scBRCA1$DF)
```

##Subcluster
###Tcell
```{r, fig.width=10}
Idents(scBRCA1) <- scBRCA1$Identity.Primary
Tcell <- subset(scBRCA1, idents = "T_cell")
DefaultAssay(Tcell) <- "integrated"
Tcell <- FindNeighbors(Tcell, dims = 1:50)
Tcell <- FindClusters(Tcell, resolution = 0.4)
Tcell <- RunUMAP(Tcell, dims = 1:30, spread =1, min.dist =0.2)

DefaultAssay(Tcell) <- "RNA"
Markers.T <- FindAllMarkers(Tcell)
Markers.T %>% group_by(cluster) %>% top_n(n=30, wt = avg_logFC)
selected.genes = c("CD3D","CD3G","CD4",
      "CD8A","CD8B","IL7R","GZMA","GZMK","CXCR4","CCR7",
      "FOXP3","TIGIT","CTLA4","IL2RA","TNFRSF4","S100A4",
      "NKG7","KLRF1","GZMB","GNLY","PRF1","CCL4","CCL5",
      "HSPA1B","HSPA1A","TNF","SPP1","APOE",
      "KLRC1","KLRD1","FCER1G","XCL1","XCL2",
      "CCR7","RPL32","RPS8","RPL39","SELL",
      "IL17F","IL17A","CCR6","CXCR6","CCL20"
      
)
DotPlot(Tcell, features = unique(selected.genes)) + scale_SummaerSea2  +Dot_scale+Dot_axis90
Idents(Tcell) <- Tcell$integrated_snn_res.0.4
Tcell <- RenameIdents(Tcell,
                      '0' = "T_CD8",
                      '1' = "Treg",
                      '2' = "NK1",
                      '3' = "Unk2",
                      '4' = "NK2",
                      '5' = "T_Rps",
                      '6' = "T_CD4"
                      )

Tcell$Identity <- factor(Idents(Tcell), levels = c("NK1","NK2","T_CD8","T_CD4","Treg","T_Rps","Unk2") )
Idents(Tcell) <- Tcell$Identity
DimPlot(Tcell)
table(Tcell$Identity, Tcell$DF)
```
####Cluster besed QC Tcell


```{r, fig.width=10}
df = FetchData(Tcell, vars = c("nCount_RNA","nFeature_RNA","percent.mt","integrated_snn_res.0.5","Identity"))
df$CG <- df$nCount_RNA/df$nFeature_RNA
ggplot(df, aes(x= Identity, y = percent.mt )) + geom_violin(scale = "width") + geom_jitter() 
ggplot(df, aes(x= Identity, y = nCount_RNA ))  + geom_violin(scale = "width") + geom_jitter() 
ggplot(df, aes(x= Identity, y = nFeature_RNA ))  + geom_violin(scale = "width") + geom_jitter() 
ggplot(df, aes(x= Identity, y = CG )) + geom_violin(scale = "width") + geom_jitter() 
```
###Myeloid
```{r}
Idents(scBRCA1) <- scBRCA1$Identity.Primary

Myeloid <- subset(scBRCA1, idents = "Myeloid")
DefaultAssay(Myeloid) <- "integrated"
Myeloid <- FindNeighbors(Myeloid, dims = 1:50)
Myeloid <- FindClusters(Myeloid, resolution = 0.4)
Myeloid <- RunUMAP(Myeloid, dims = 1:30, spread =1, min.dist =0.2)
DefaultAssay(Myeloid) <- "RNA"

Markers.M <- FindAllMarkers(Myeloid) 
Markers.M %>% group_by(cluster) %>% top_n(n=30, wt = avg_logFC)

selected.genes = c("C1QA","C1Qb","CD83","CCL3","CCL4","CXCL8",
                   "OLR1","VEGFA","CXCR4","AREG","RGCC","CCL20","CXCL10",
                   "CD1C","CD1E","CLEC10A","HLA-DQA1","HLA-DQB1",
                   "SPP1","APOE","LGALS1","IFI6","IFI27","IFIT1",
                   "S100A8","S100A9","VCAN","CSF3R",
                   "FCGR3A","	ADGRE5","LYST","ADGRE1")

DotPlot(Myeloid, features = unique(selected.genes)) + scale_SummaerSea2  +Dot_scale+Dot_axis90

Myeloid <- RenameIdents(Myeloid,
                      '0' = "Mono_Complement",
                      '1' = "Mono_VEGFA",
                      '2' = "Mono_APC",
                      '3' = "Mono_SPP1",
                      '4' = "Mono_PMN-like",
                      '5' = "TAM"
                      )
Myeloid$Identity <- Idents(Myeloid)
DimPlot(Myeloid)
table(Myeloid$Identity, Myeloid$DF)
```

```{r}
#selected.genes = c("CD14",sort(find("FCG")), "CSF1R","CSF2RA","CSF2RB","CSF3R","ADGRE1")
#selected.genes = sort(find("HLA-"))
#selected.genes = c("C1QB","C1QC","CCL3","CCL4","VCAN","SPP1","VEGFA","S100A8","THBS1","LYZ")


for(i in selected.genes ){
      print(
            VlnPlot(Myeloid, features = i)
      )
}
for(i in selected.genes ){
      print(
           FeaturePlot(Myeloid, features = i )  + scale_SummaerSea2 
      )
}
tmp = FindMarkers(Myeloid, ident.1 = c(0,3), ident.2 = c(1,2,4))
tmp %>% arrange(avg_logFC)


```

##Transfer Identity
```{r, fig.width=10}
tmp = scBRCA1[[]] %>% as_tibble(rownames = "CB") %>% dplyr::select(CB, Identity.Primary) %>% filter(!Identity.Primary %in% c("T_cell","Myeloid"))
colnames(tmp) = c("CB","Identity")
tmp2 = Tcell[[]] %>% as_tibble(rownames = "CB") %>% dplyr::select(CB, Identity)
tmp3 = Myeloid[[]] %>% as_tibble(rownames = "CB") %>% dplyr::select(CB, Identity)
tmp = rbind(tmp,tmp2,tmp3)
label = tmp$Identity
names(label )=tmp$CB
scBRCA1 <- AddMetaData(scBRCA1, metadata = label, col.name = "Identity")
sort(levels(as.factor(scBRCA1$Identity)))
level1 = c("cDC1","cDC2","pDC",
           "NK1","NK2","T_CD8","T_CD4","Treg","T_Rps","T_Proliferating",
           "Mono_Complement","Mono_VEGFA","Mono_APC","Mono_SPP1","Mono_PMN-like",
           "TAM",
           "B_cell","Mast_cell","Endothelial",
           "Unk1","Unk2","LQ")

scBRCA1$Identity <- factor(scBRCA1$Identity, levels = level1)
scBRCA1$Identity.rev <- factor(scBRCA1$Identity, levels = rev(level1) )
Idents(scBRCA1) <- scBRCA1$Identity
DimPlot(scBRCA1, label = T)


```

##Signature
```{r, fig.width=10}
Markers.list = list(
      "DC" = c("CLEC9A","BATF3","XCR1","IRF8",
               "CD1E","CD1A","HLA-DQA2","HLA-DQB2","CD207",
                "LILRA4","IRF7","CLEC4C"),
      "NK1" = c("NKG7","KLRF1","GZMB","GNLY","PRF1","CCL4","CCL5","IFNG"),
      "NK2" = c("KLRC1","KLRD1","FCER1G","XCL1","XCL2"),
      "T" = c("CD3D","CD3G","CD4"),
      "CD8" = c("CD8A","CD8B","IL7R","GZMA","GZMK","CXCR4","CCR7"),
      "CD4" = c("IL17F","IL17A","CCR6","CXCR6","CCL20"),
      "Treg" = c("FOXP3","TIGIT","CTLA4","IL2RA","TNFRSF4","S100A4"),
      "T_Rps" = c("CCR7","RPL32","RPS8","RPL39","SELL"),
      "T_Pro" = c("MKI67","CDK1"),
      "Mono1" = c("C1QA","C1QB","CD83","CCL3","CCL4","CXCL8"),
      "Mono2" = c("OLR1","VEGFA","CXCR4","AREG","RGCC","CCL20","CXCL10"),
      "Mono3" = c("CD1C","CD1E","CLEC10A","HLA-DQA1","HLA-DQB1"),
      "Mono4" = c("SPP1","APOE","LGALS1","IFI6","IFI27","IFIT1"),
      "Mono5" = c("S100A8","S100A9","VCAN","CSF3R"),
      "TAM" = c("FCGR3A","ADGRE5","LYST","ADGRE1"),
      "B" = c("IGHM","CD79A","IGHD"),
      "Mast" = c("TPSB2","KIT","HDC","CSF1"),
      "Endo" = c("VWF","COL4A1","PECAM1"),
      "Unk1" = c("AL022069.1","AC087239.1","HSPA2","PLK2"),
      "Unk2" = c("HSPA1B","HSPA1A","TNF","SPP1","APOE"),
      "Other" = c("S100A14","KRT8","KRT18","KRT19","PTGS1","PTGS2","PTGER2","PTGER4")
      
)
selected.genes <- unlist(Markers.list)
Idents(scBRCA1) <- scBRCA1$Identity.rev
for(i in 1){
      png(filename = fig("DotPlot.SignatureGene"), width = 20, height = 8,units = "in", res =200)
      print(
            DotPlot(scBRCA1, features = unique(selected.genes) ) + scale_SummaerSea2  +Dot_scale+Dot_axis90 +
                  theme(legend.position = "bottom")
      )
      dev.off()
}
VlnPlot(scBRCA1, features = "IFNG")
DotPlot(scBRCA1, features = unique(selected.genes)) + scale_SummaerSea2  +Dot_scale+Dot_axis90

saveRDS(scBRCA1, file = "/yshare1/ZETTAI_path_WA_slash_home_KARA/home/siwakorn/BRCA/RDS/scBRCA1.DecontXNativeFilterd.Count500Mt10.Identity.210413.rds" )

AllMarkers <- readRDS(file = "/yshare1/ZETTAI_path_WA_slash_home_KARA/home/siwakorn/BRCA/RDS/AllMarkers.scBRCA1.DecontXNativeFilterd.Count500Mt10.Identity.210413.rds")
AllMarkers %>% group_by(cluster) %>% top_n(n=50, wt=avg_logFC) %>% filter(cluster == "pDC")
```

#---Analysis---
##EP4 sorting enrichment
```{r}
num = table(scBRCA1$Identity, scBRCA1$orig.ident) %>% as.matrix()
pc = apply(num, 1, function(x) x/colSums(num)*100) %>% t() %>% as.data.frame() %>% as_tibble(rownames = "Identity")
pc$Change <- (pc$EP4 - pc$CD45 ) /pc$CD45*100 %>% round(digits = 3)
pc$Change <-  round(pc$Change, digits = 2)
pc$position <- pc$Change
pc$position[pc$position > 0] <- pc$position[pc$position > 0]  + 2
pc$position[pc$position < 0] <- 0.5
pc
pc$Identity <- factor(pc$Identity, levels = level1)
ggplot(pc, aes(x= Identity, y =Change ))+
      geom_col()+
      geom_text(aes(x=Identity, y = position, label =Change ), angle = 90, hjust = -1)+
      theme_classic()+
      theme(axis.text = element_text(color= "black"),
            axis.text.x = element_text(angle = 90, vjust = 0.3, hjust =1),
            axis.title.x = element_blank()
            )


```

##DE EP4-CD45 sample
```{r}
DE.list <- list()
Idents(scBRCA1) <- scBRCA1$Identity
for(i in levels(Idents(scBRCA1))){
      tryCatch({
            tmp = subset(scBRCA1, idents = i )
            Idents(tmp) <- tmp$orig.ident
            levels(as.factor(scBRCA1$orig.ident ))
            DE.list[[i]] = FindMarkers(tmp, ident.1 = "EP4", ident.2 = "CD45", logfc.threshold = 0.01)
      },
      error = function(e){print(e)}
      )
}

#saveRDS(DE.list, file = "/yshare1/ZETTAI_path_WA_slash_home_KARA/home/siwakorn/BRCA/RDS/scBRCA1.DecontXNativeFilterd.Count500Mt10.Identity.210413.DElist.EP4xCD5.rds" )

DimPlot(scBRCA1, label =T) +NoLegend()
DimPlot(tmp)
DefaultAssay(tmp) <- "RNA"
tmp <- NormalizeData(tmp)
VlnPlot(tmp, features = "IRF7")

i="pDC"
DE.list[[i]] %>% arrange(desc(avg_logFC) ) %>% filter(pct.1 > 0.7)
DE.list[[i]] %>% arrange(avg_logFC) 
VlnPlot(scBRCA1, features ="PTGER4", split.by = "orig.ident", pt.size = 0) + NoLegend()
```


#Identity
```{r}
scBRCA1 <- RenameIdents(scBRCA1, 
                        '0' = "T_cell",
                        '1' = "T_cell",
                        '2' = "Myeloid",
                        '3' = "T_cell",
                        '4' = "Myeloid",
                        '5' = "Myeloid",
                        '6' = "Myeloid",
                        '7' = "Myeloid",
                        '8' = "T_cell",
                        '9' = "T_cell",
                        '10' = "Mast_cell",
                        '11' = "Myeloid",
                        '12' = "T_cell",
                        '13' = "T_cell",
                        '14' = "cDC2",
                        '15' = "T_cell",
                        '16' = "cDC1",
                        '17' = "B_cell",
                        '18' = "Endothelial",
                        '19' = "T_cell",
                        '20' = "pDC",
                        '21' = "LQ",
                        '22' = "Epithelial"
                        )
scBRCA1$Identity.primary <- Idents(scBRCA1)
DimPlot(scBRCA1X, label =T)
col.Identity.Primary = c("#00A6A6","#f49f0a","#457B9D","#1D3557","#C62E65","#9300b3","#806D40","#FE4A49","#FED766","#E6E6EA")
```

```{r}
Idents(scBRCA1) <- scBRCA1$DecontX
levels(as.factor(scBRCA1$DecontX))
scBRCA1X <- subset(scBRCA1, idents = c("No","NaiveFiltered"))
Idents(scBRCA1X) <- scBRCA1X$Identity.primary
```

```{r}
DefaultAssay(scBRCA1X) <- "integrated"
scBRCA1X <- RunUMAP(scBRCA1X, dims =1:30, spread = 1, min.dist = 0.5)
DimPlot(scBRCA1X,label = T)
saveRDS(scBRCA1X, file = "/yshare1/ZETTAI_path_WA_slash_home_KARA/home/siwakorn/BRCA/RDS/scBRCA1.Integration.3DeconxCondition.210406.RemoveDecont500Mt10.rds")

DefaultAssay(scBRCA1X) <- "RNA"
Markers <- FindAllMarkers(scBRCA1X)
Markers  %>% group_by(cluster) %>% top_n(n=30, wt =avg_logFC)
#saveRDS(Markers, file = "/home/siwakorn/BRCA/RDS/scBRCA1.Integration.3DeconxCondition.210406.RemoveDecont500Mt10.Markers.Identity.primary.rds")
selected.genes = c("CD3D","CD3G","CCL5","GZMA","NKG7","CD14","LYZ","S100A9","C1QC","IL1B",
                   "CLEC9A","BATF3","XCR1","IRF8","CD1E","CD1A","HLA-DQA2","HLA-DQB2","CD207",
                   "LILRA4","IRF7","CLEC4C",
                   "IGHM","CD79A","IGHD",
                   "TPSB2","KIT","HDC","CSF1",
                   "VWF","COL4A1","PECAM1",
                   "S100A14","KRT8","KRT18","KRT19",
                   "AL022069.1","AC087239.1","HSPA2","PLK2")
                   "PTGS1","PTGS2","PTGER2","PTGER4")
sort(levels(scBRCA1X$Identity.primary))
tmp = c("T_cell","Myeloid","cDC1","cDC2","pDC","B_cell","Mast_cell","Endothelial","Epithelial","LQ")
scBRCA1X$Identity.primary = factor(scBRCA1X$Identity.primary, levels = tmp)
scBRCA1X$Identity.primary.rev = factor(scBRCA1X$Identity.primary, levels = rev(tmp) )
Idents(scBRCA1X) <- scBRCA1X$Identity.primary.rev
DefaultAssay(scBRCA1X)

Idents(scBRCA1X) <- scBRCA1X$Identity.primary
for(i in 1){
      png(filename = "/home/siwakorn/BRCA/Fig/210407_IdentityPrimary_DecontXComparison/scBRCA1.Identity.Primary.DM.210407.png", width = 6, height = 6,units = "in", res =200)
      print(
            DimPlot(scBRCA1X, label = T, cols = col.Identity.Primary, repel = T)   + NoLegend()
      )
      dev.off()
}
Idents(scBRCA1X) <- scBRCA1X$Identity.primary.rev
scBRCA1X2 <- subset(scBRCA1X, idents = setdiff(levels(Idents(scBRCA1X)), "LQ" ) )
Idents(scBRCA1X2) <- scBRCA1X2$Identity.primary.rev
for(i in 1){
      png(filename = "/home/siwakorn/BRCA/Fig/210407_IdentityPrimary_DecontXComparison/scBRCA1.Identity.Primary.Dotplot.210407.png", width = 14, height = 7,units = "in", res =200)
      print(
            DotPlot(scBRCA1X, features = selected.genes) + scale_SummaerSea2  +Dot_scale+Dot_axis90
      )
      dev.off()
}

m=1
for(i in selected.genes){
       png(filename = paste0("/home/siwakorn/BRCA/Fig/210407_IdentityPrimary_DecontXComparison/scBRCA1.Identity.Primary.FP.",m,".",i,".210407.png"), 
           width = 6, 
           height = 6,units = "in", res =200)
      print(FeaturePlot(scBRCA1X, features = i, ) + scale_SummaerSea2  +Dot_scale+Dot_axis90 )
      dev.off()
      m=m+1
}
```



#Compare DecontX result
```{r}
Tcell <- subset(scBRCA1X, idents = "T_cell")
Idents(Tcell) <- Tcell$orig.ident
levels(Idents(Tcell))
Tcell2 <- subset(Tcell, idents = "CD45" )
Idents(Tcell2) <- Tcell2$DecontX
levels(Idents(Tcell2))
DE1 <- FindMarkers(Tcell2, ident.1 = "No", ident.2 = "NaiveFiltered", logfc.threshold = 0.01)
DE1 <- arrange(DE1, desc(avg_logFC))
DE1$used <- c(rep("Label",10),rep("Unlabel",nrow(DE1)-20), rep("Label",10) )
DE1$logPvalue = (-1)*log(DE1$p_val,base=1000)
tmp = as_tibble(DE1, rownames = "Gene")
 
 for(i in 1){
    png(filename = fig(paste0("Volcano.Tcell.None-NaiveFiltered.log1000.")), width = 7, height = 8, units="in",res=200)
    border = max(tmp$avg_logFC,-(min(tmp$avg_logFC)) )
    print(
      ggplot(tmp, aes(x = avg_logFC, y = logPvalue, color = used, size = used )) + 
        geom_point() +
        scale_color_manual(values = c("firebrick2","black"))+ #select gray65 or black
        scale_size_manual(values = c( 1.5, 0.75) ) +
        theme_linedraw(base_size = 40)+
        theme(text=element_text(size = 12))+
        geom_vline(xintercept = c(-0.3,0.3)) +
        geom_hline(yintercept = c(2)) +
        xlim(-border,border) +
        ylab("- log1000(p-value)") +
        geom_text_repel(size =6,fontface ="bold", data = subset(tmp, used == "Label"),aes(label = Gene, hjust = 1.2)) +
        NoLegend()
      )
  dev.off()
 }
table(scBRCA1$orig.ident, scBRCA1$DecontX)
```


```{r}
Idents(scBRCA1X) <- scBRCA1X$Identity.primary
cDC2 <- subset(scBRCA1X, idents = "cDC2")
Idents(cDC2) <- cDC2$orig.ident
cDC2 <- subset(cDC2, idents = "CD45")

Idents(cDC2) <- cDC2$DecontX
levels(Idents(cDC2))
DE2 <- FindMarkers(cDC2, ident.1 = "No", ident.2 = "NaiveFiltered", logfc.threshold = 0.01)
DE2 <- DE2 %>% arrange(desc(avg_logFC))
DE2$used <- c(rep("Label",10),rep("Unlabel",nrow(DE2)-20), rep("Label",10) )
DE2$logPvalue = (-1)*log(DE2$p_val,base=10)
tmp = as_tibble(DE2, rownames = "Gene")
tmp

 for(i in 1){
    png(filename = fig(paste0("Volcano.cDC2.None-NaiveFiltered.")), width = 7, height = 8, units="in",res=200)
    border = max(tmp$avg_logFC,-(min(tmp$avg_logFC)) )
    print(
      ggplot(tmp, aes(x = avg_logFC, y = logPvalue, color = used, size = used )) + 
        geom_point() +
        scale_color_manual(values = c("firebrick2","black"))+ #select gray65 or black
        scale_size_manual(values = c( 1.5, 0.75) ) +
        theme_linedraw(base_size = 40)+
        theme(text=element_text(size = 12))+
        geom_vline(xintercept = c(-0.3,0.3)) +
        geom_hline(yintercept = c(2)) +
        xlim(-border,border) +
        ylab("- log10(p-value)") +
        geom_text_repel(size =6,fontface ="bold", data = subset(tmp, used == "Label"),aes(label = Gene, hjust = 1.2)) +
        NoLegend()
      )
  dev.off()
}
```

#Seperate dataset
```{r}
Idents(scBRCA1) <- scBRCA1$DecontX
levels(Idents(scBRCA1))
naive <- subset(scBRCA1, idents = "No")
naive
Decon <- subset(scBRCA1, idents = "NaiveFiltered")
Decon

DefaultAssay(naive) = "integrated"
naive <- RunUMAP(naive, dim = 1:30, spread =1 ,min.dist = 0.5)
Idents(naive) <- naive$Identity.primary
DimPlot(naive)

DefaultAssay(Decon) = "integrated"
Decon <- RunUMAP(Decon, dim = 1:30, spread =1 ,min.dist = 0.5)
Idents(Decon) <- Decon$Identity.primary
DimPlot(Decon)

for(i in 1){
      png(filename = "/home/siwakorn/BRCA/Fig/210407_IdentityPrimary_DecontXComparison/scBRCA1.Identity.Primary.Decon.DM.210407.png", width = 6, height = 6,units = "in", res =200)
      print(
            DimPlot(Decon, label = T, cols = col.Identity.Primary, repel = T)   + NoLegend()
      )
      dev.off()
}

for(i in c(selected.genes) ){
       png(filename = paste0("/home/siwakorn/BRCA/Fig/210407_IdentityPrimary_DecontXComparison/scBRCA1.Identity.Primary.FP.Naive.",m,".",i,".210407.png"), 
           width = 6, 
           height = 6,units = "in", res =200)
      print(FeaturePlot(naive, features = i, ) + scale_SummaerSea2  +Dot_scale+Dot_axis90 )
      dev.off()
        png(filename = paste0("/home/siwakorn/BRCA/Fig/210407_IdentityPrimary_DecontXComparison/scBRCA1.Identity.Primary.FP.Decon.",m,".",i,".210407.png"), 
           width = 6, 
           height = 6,units = "in", res =200)
      print(FeaturePlot(Decon, features = i, ) + scale_SummaerSea2  +Dot_scale+Dot_axis90 )
      dev.off()
}
DefaultAssay(naive) = "RNA"
DefaultAssay(Decon) = "RNA"
for(i in c("PTGER2","PTGER4")){
       png(filename = paste0("/home/siwakorn/BRCA/Fig/210407_IdentityPrimary_DecontXComparison/scBRCA1.Identity.Primary.naive.",i,".210407.png"), 
           width = 6, 
           height = 3,units = "in", res =200)
      print(VlnPlot(naive, features = i, pt.size =0.2) )
      dev.off()
        png(filename = paste0("/home/siwakorn/BRCA/Fig/210407_IdentityPrimary_DecontXComparison/scBRCA1.Identity.Primary.Decon.",i,".210407.png"), 
           width = 6, 
           height = 3,units = "in", res =200)
      print(VlnPlot(Decon, features = i,  pt.size =0.2) )
      dev.off()
}

DotPlot(naive, features = c("HLA-DPA1","HLA-DPB1","APOE","HLA-DRB1") )
Vln
```

